From Education to Entrepreneurship

### 2014-12-12 index.Rmd
Organization of repository

# Create a vector of packages used
pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv', 'Zelig',
          'stargazer', 'Amelia')

>>>>

# Create a vector of packages used
pkgs <- c('repmis', 'ggvis', 'devtools', 'googleVis', 'countrycode', 'reshape2', 'shiny', 'httpuv')
